%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   Filename    : appendix_D.tex 
%
%   Description : This file is one of the appendices. 
%                 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section{Sample Children's Story Modification}
\label{sec:appendixc}

As mentioned in Chapter 1, each children's story in the corpus undergo different types of modifications to simulate different scenarios or story formats. And in order to illustrate the different modifications, here is an unmodified excerpt from one of the stories already in the corpus entitled ``A Wild Weather Day".

	\noindent
	\hspace{1 in}\emph{It was a wild and windy day. The JumpStart ship was headed for Tree Fort Island.} \\
	\hspace*{1 in}\emph{Frankie was at the wheel. The sails flapped in the wind. The ship raced through the water.} \\
	\hspace*{1 in}\emph{``Why are we going so fast?" Pierre asked. ``The wind is blowing us along on our adventure," CJ said. ``Did you know that wind is just air that is strong and fast?"} \\
	\hspace*{1 in}\emph{``Like Frankie!" Pierre said. ``He's strong and fast, too."} \\
	\hspace*{1 in}\emph{``Why is the sky getting so dark?" Pierre asked.}\\
	\hspace*{1 in}\emph{``I know why it's dark!" Eleanor said. ``Clouds get dark when they fill up with tiny drops of water."} \\
	\hspace*{1 in}\emph{``Look! They're almost the same color as your bow," Pierre said.} \\
	\hspace*{1 in}\emph{A big drop of rain fell on Pierre's nose. ``Oh, no!" he said. ``It's starting to rain!"} \\
	\hspace*{1 in}\emph{``The rain is coming from the clouds," CJ said.} \\
	\hspace*{1 in}\emph{``The water in tne clouds got too heavy, and now it's falling down on us!"} \\
	\hspace*{1 in}\emph{``Just like when Hopsalot waters his garden," said Pierre.} \\

The first type of modification is done by transforming the dialogues into declarative sentences. Here is the modified version of the excerpt above:

	\noindent
	\hspace{1 in}\emph{It was a wild and windy day. The JumpStart ship was headed for Tree Fort Island.} \\
	\hspace*{1 in}\emph{Frankie was at the wheel. The sails flapped in the wind. The ship raced through the water.} \\
	\hspace*{1 in}\emph{They are going so fast. The wind is blowing them along on their adventure. The wind is just air that is strong and fast.} \\
	\hspace*{1 in}\emph{Frankie is like the wind. He's strong and fast, too.} \\
	\hspace*{1 in}\emph{The sky is getting so dark.}\\
	\hspace*{1 in}\emph{Eleanor knows why it is dark. Clouds get dark when they fill up with tiny drops of water.} \\
	\hspace*{1 in}\emph{They are almost the same color as Eleanor's bow.} \\
	\hspace*{1 in}\emph{A big drop of rain fell on Pierre's nose. It is starting to rain!} \\
	\hspace*{1 in}\emph{The rain is coming from the clouds.} \\
	\hspace*{1 in}\emph{The water in the clouds got too heavy, and now it is falling down on them!} \\
	\hspace*{1 in}\emph{Just like when Hopsalot waters his garden.} \\

The second type is the usual transformation of direct to indirect speech. 

	\noindent
	\hspace{1 in}\emph{It was a wild and windy day. The JumpStart ship was headed for Tree Fort Island.} \\
	\hspace*{1 in}\emph{Frankie was at the wheel. The sails flapped in the wind. The ship raced through the water.} \\
	\hspace*{1 in}\emph{Pierre asked why they were going so fast. CJ said that the wind was blowing them along on their adventure. He also asked if they know that wind is just air that is strong and fast.} \\
	\hspace*{1 in}\emph{Pierre said like Frankie. Pierre said that Frankie was strong and fast, too.} \\
	\hspace*{1 in}\emph{Pierre asked why the sky was getting so dark.}\\
	\hspace*{1 in}\emph{Eleanor said that she knew why it is dark. She explained that clouds get dark when they fill up with tiny drops of water.} \\
	\hspace*{1 in}\emph{Pierre said look! They are almost the same color as Eleanor's bow.} \\
	\hspace*{1 in}\emph{A big drop of rain fell on Pierre's nose. He was shocked. It is starting to rain.} \\
	\hspace*{1 in}\emph{CJ said that the rain is coming from the clouds.} \\
	\hspace*{1 in}\emph{The water in the clouds got too heavy, and now it is falling down on them.} \\
	\hspace*{1 in}\emph{Pierre said that it is just like when Hopsalot waters his garden.} \\
	
While modifying, there may be cases wherein a specific sentence or a line uttered by a character will be omitted. Such sentences can be interjections like ``Oh my!" and ``Alas!".